cardinalR: Generating interesting high-dimensional data structures

### 2025-09-16 paper-cardinalR.Rmd
Added r_hole

Finally, we consider a cube that has a central spherical hole. This is generated using the `gen_cubehole(n, p)` function. The cube is generated as per the uniformly distributed cube, but points inside sphere of radius $0.5$ are removed, resulting in a hollow cube structure (`r knitr::asis_output(if (knitr::is_html_output()) { "Figure \\@ref(fig:cube) c"} else { "Figure \\@ref(fig:cube-proj) c"})`).

@@

```{r data-cubehole, echo=TRUE}
cubehole <- gen_cubehole(n = 3000, p = 4)
```

>>>>

Finally, we consider a cube that has a central spherical hole. This is generated using the `gen_cubehole(n, p, r_hole)` function. The cube is generated as per the uniformly distributed cube, but points inside sphere of radius (`r_hole`) are removed, resulting in a hollow cube structure (`r knitr::asis_output(if (knitr::is_html_output()) { "Figure \\@ref(fig:cube) c"} else { "Figure \\@ref(fig:cube-proj) c"})`).

@@

```{r data-cubehole, echo=TRUE}
cubehole <- gen_cubehole(n = 3000, p = 4, r_hole = 0.5)
```

### 2025-09-16 paper-cardinalR.tex
Added r_hole

Finally, we consider a cube that has a central spherical hole. This is generated using the \texttt{gen\_cubehole(n,\ p)} function. The cube is generated as per the uniformly distributed cube, but points inside sphere of radius \(0.5\) are removed, resulting in a hollow cube structure (Figure \ref{fig:cube-proj} c).

@@

\begin{verbatim}
cubehole <- gen_cubehole(n = 3000, p = 4)
\end{verbatim}

>>>>

Finally, we consider a cube that has a central spherical hole. This is generated using the \texttt{gen\_cubehole(n,\ p,\ r\_hole)} function. The cube is generated as per the uniformly distributed cube, but points inside sphere of radius (\texttt{r\_hole}) are removed, resulting in a hollow cube structure (Figure \ref{fig:cube-proj} c).

@@

\begin{verbatim}
cubehole <- gen_cubehole(n = 3000, p = 4, r_hole = 0.5)
\end{verbatim}
